Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-20 Draft.Rmd
aic

```{r}
library(tidyverse)
library(tidymodels)
library(broom)
library(caret)
library(plotROC)

@@

# Create standardize train data for kNN

@@

## Models 
```{r Linear Regression}
set.seed(123)
# Create the recipe for all models
rec <- train %>% 
    recipe(value ~ lat + lon + state)

@@

```{r Boost}
set.seed(123)
# Preprocessing "recipe"
preprocessing_recipe <- 
  recipes::recipe(value~lon+lat, data = training(dat_split)) %>%
  # Convert categorical variables to factors
  recipes::step_string2factor(all_nominal()) %>%
  # Combine low frequency factor levels
  recipes::step_other(all_nominal(), threshold = 0.01) %>%
  # Remove no variance predictors which provide no predictive information 
  recipes::step_nzv(all_nominal()) %>%
  prep()

>>>>

```{r}
library(tidyverse)
library(tidymodels)
library(broom)
library(caret)
library(plotROC)
library(vip)

@@

# Create standardize train data for kNN and PCA

@@

## Models 
```{r Lin Regr.}
rec1 <- recipe(value ~ ., data = train) %>% 
                      step_YeoJohnson(all_numeric(), -all_outcomes()) %>% 
                      step_normalize(all_numeric(), -all_outcomes())

model1 <- linear_reg() %>% 
    set_engine("lm") %>% 
    set_mode("regression")

fit1 = model1 |> fit(value ~ ., data=train)
summary(fit1$fit)

tidy(fit1)
glance(fit1)
vip(fit1)

wf1 <- workflow() %>% 
    add_recipe(rec1) %>% 
    add_model(model1)

res1 = wf1 |> last_fit(split=dat_split)
res1 |> collect_metrics()

library(MASS)
fit <- lm(value ~ .,data=train)
step <- stepAIC(fit, direction="both")
step$anova

```{r Linear Regression}
set.seed(123)
# Create the recipe for all models
rec <- train %>% 
    recipe(value ~ lat + lon + state)

@@

```{r Xgboost}
set.seed(123)
# Preprocessing "recipe"
preprocessing_recipe <- 
  recipes::recipe(value~lon+lat, data = training(dat_split)) %>%
  # Convert categorical variables to factors
  recipes::step_string2factor(all_nominal()) %>%
  # Combine low frequency factor levels
  recipes::step_other(all_nominal(), threshold = 0.01) %>%
  # Remove no variance predictors which provide no predictive information 
  recipes::step_nzv(all_nominal()) %>%
  prep()
